Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2015-04-27 experiments.tex
ACM camera ready

To evaluate and compare the performance indexes of different
architectures for a specific application, one needs to simulate the
architecture running the code of the application. To make
architectural exploration possible both the compiler and the simulator
have to be retargetable. The open source project Trimaran~\cite{trimaran_hp} provides these
tools and, together with the estimation framework \ee~\cite{palpatti_estimedia03}, has been
adopted as a tested and flexible platform for carrying out the
experiments.

@@

Together with the configuration of the system, the statistics produced
by simulation contain all the information needed to apply the area,
performance and power consumption estimation model implemented in the
\emph{Estimator} component. These are high-level abstraction models
that allow to quickly get an estimation while still providing a
discrete level of accuracy (for a detailed description of the models
see also~\cite{palpatti_estimedia03}).

>>>>

To evaluate and compare the performance indexes of different
architectures for a specific application, one needs to simulate the
architecture running the code of the application. To make
architectural exploration possible both the compiler and the simulator
have to be retargetable. The open source project Trimaran~\cite{trimaran_hp} provides these
tools and, together with the estimation framework
\ee~\cite{Ascia2005940}, has been
adopted as a tested and flexible platform for carrying out the
experiments.

@@

Together with the configuration of the system, the statistics produced
by simulation contain all the information needed to apply the area,
performance and power consumption estimation model implemented in the
\emph{Estimator} component. These are high-level abstraction models
that allow to quickly get an estimation while still providing a
discrete level of accuracy (for a detailed description of the models
see also~\cite{Ascia2005940}).
